### 2017-02-13 chapters/ch2-checkpoint.tex
Notes on random sampling

@@

\subsection{Random sampling}

>>>>

\subsection{Promoter invitation}
The output of promoter registration is a random set of $N$ promoters. If 1/3 of
the population is malicious, then we cannot guarantee that the chosen promoters
satisfy the $< n/3$ requirement.

Promoter invitation is an attempt to involve human in the protocol. A naive
method method is to use $N$ tickets, and then distribute them to trusted nodes.
Nodes with the ticket can forward it to others. We have to rely on the humans to
always forward the tickets to other honest humans. Finally, the nodes that hold
a ticket are promoters. The result is that we have a permissioned system.

@@

Node $i$ may wish to perform existence testing for all its unverified TX blocks.

\subsection{Random sampling}
Existence testing detects fraud when a single party of the TX is malicious. To
detect fraud when both parties are malicious, every node performs existence
testing on all TX blocks between CP blocks as if they are some other node. The
assignment is determined using CP block digest where every node is assigned to
the nearest node that has a higher digest, cycle back if there is no higher
digest.

If the number of malicious parties is low, then it's more probable that a fork
is detected. If where there are a large number of malicious parties, we repeat
the random sampling process.
